A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 subarchitectures/planner.sa/trunk/src/latex/AAAI11/conc.tex
more change

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a base planner that
switches between fast sequential and expensive decision-theoretic
planning. Given a DTPDDL model of the environment, sequential planning
is used to compute an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until testing of an assumption about the runtime state is
scheduled. At that point a DT session performs some sensing
which determines whether or not the sequential session should be
allowed to continue, or otherwise acts to achieve the overall
objectives. We find our approach performs quickly and relatively
efficiently in a number of large real-world task and observation
planning problems.

>>>>

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a planner that
switches between fast sequential and expensive DT planning. Given a
DTPDDL model of the environment, sequential planning is used to
compute an initial deterministic sequential plan and complementary
runtime evolution of the decision process. That plan is executed until
testing of an assumption about the runtime state is scheduled. At that
point a DT session performs some sensing which determines whether or
not the sequential session should be allowed to continue, or otherwise
acts to achieve the overall objectives. We find our approach performs
quickly and relatively efficiently in a number of large real-world
task and observation planning problems.
